\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

\section{Results}\label{section:results}

\subsection{Model Validation}

Starting from a simple case as this is described in fig. \ref{fig:square}, there is a simple square shape formation consisted of 2 values of different (K) permeabilities (blue and red shaded square areas). The domain is fully saturated with fluid $2$. We inject fluid $1$ across the left hand side of the formation and we are trying to displace the existing fluid $2$. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$ and a main finger starts to appear.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}\label{section:results}

\subsection{Model Validation}
Initially a case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}. A simple square shape formation consisted of$4$ square regions that each one has $2$ values of different permeabilities (K is represented by the blue and red shaded square areas). The aspect ratio of the domain is $1$ and is fully saturated with fluid $2$. At the upper and lower sides of the domain no-slip boundary condition is applied, meaning there is no mass transport in and out of the domain. The left hand side of the domain is defined as the inlet for fluid $1$ with a velocity of $u=1$ while the right hand side is the outlet and pressure is set to $0$. Fluid $1$ across the left hand side of the formation is trying to displace the existing fluid $2$. What can been seen here is a cross flow case as the flow passes through different regions and develops. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$.

@@

\section{Conclusions}
